\ProjectName{}: Data Imputation as a Query Optimization

### 2017-02-23 paper/relatedwork.tex
Add related work items

>>>>

In \cite{wolf2007query}, queries over databases with missing values are
processed in a statistical approach, taking advantage of correlations between
variables. Both tuples that match the original query as well as a ranking of
tuples with incomplete data that may match are returned. Our work differs in
that we allow any well-formed statistical technique to be used for imputation
and focus on returning results to the analyst as if the database had been
complete.

Designers of data stream processing systems frequently confront missing values
and consider them carefully in query processing. Often, if sensor error is the
cause of missing values, values can be imputed with high confidence. In
\cite{fernandez2009inter}, feedback punctuation is used to dynamically
reconfigure the query plan as data continue to arrive for state-dependent
optimizations. In this framework, expensive imputations can be avoided as
real-time conditions change.
